Longitudinal Principal Manifold Estimation

### 2024-04-04 paper/main.tex
update results for 2-year duration threshold

\begin{table}[ht]
  \centering
  \begin{tabular}{|c c c c c|}
    \hline
    Structure & Regression-Adjusted & Data & LPME & PME  \\
    \hline
    Left Hippocampus & No & 218 & 225 & \textbf{191} \\
    Right Hippocampus & No & 221 & 245 & \textbf{195} \\
    Left Hippocampus & Yes & 184 & 197 & \textbf{160} \\
    Right Hippocampus & Yes & 185 & 215 & \textbf{163} \\
    Left Thalamus & No & 82.9 & \textbf{49.7} & 72.0 \\
    Right Thalamus & No & 147 & \textbf{116} & 130 \\
    Left Thalamus & Yes & 68.3 & \textbf{30.7} & 57.9 \\
    Right Thalamus & Yes & 124 & \textbf{89.9} & 109 \\
    \hline
  \end{tabular}
  \caption{Mean of the empirical standard deviation of volume estimates computed for each ADNI participant. Entries that were not regression-adjusted include computations for raw volume estimates, while regression-adjusted entries compute the standard deviations of linear regression models regressing the volume estimates on time. }
  \label{table:adni_volume_sds}
\end{table}

>>>>

\begin{table}[ht]
  \centering
  \begin{tabular}{|c c c c c|}
    \hline
    Structure & Regression-Adjusted & Data & LPME & PME  \\
    \hline
    Left Hippocampus & No & 213 & 225 & \textbf{187} \\
    Right Hippocampus & No & 210 & 236 & \textbf{186} \\
    Left Hippocampus & Yes & 173 & 190 & \textbf{150} \\
    Right Hippocampus & Yes & 174 & 206 & \textbf{154} \\
    Left Thalamus & No & 78.3 & \textbf{49.0} & 67.8 \\
    Right Thalamus & No & 139 & \textbf{112} & 122 \\
    Left Thalamus & Yes & 62.8 & \textbf{29.0} & 53.0 \\
    Right Thalamus & Yes & 115 & \textbf{85.3} & 99.9 \\
    \hline
  \end{tabular}
  \caption{Mean of the empirical standard deviation of volume estimates computed for each ADNI participant. Entries that were not regression-adjusted include computations for raw volume estimates, while regression-adjusted entries compute the standard deviations of linear regression models regressing the volume estimates on time. }
  \label{table:adni_volume_sds}
\end{table}
